### 2021-06-18 paper/model/policies.tex
Merge policies and endogenous contact reductions.

>>>>

Not all things that reduce contacts compared to the pre-pandemic level are driven
by NPIs. Therefore, we also model endogenous contact reductions that can depend on
the health state of individuals, known risk contacts or the local incidence of
infections. Examples are strong contact reductions for symptomatic individuals or those
who have a positive PCR or rapid tests or contact reductions when a houshold member
tested positive. The extent to which contacts are reduced can be calibrated from
surveys. For an application of our model showcasing private contact tracing in the
context of the Christmas holidays see \cite{Gabler2020}.
